Large Language Models in Reinforcement Learning - A Comparison of Methods

### 2023-10-03 doc/paper.tex
update paper
Signed-off-by: Jonatan Hanssen <jonatan.hanssen@outlook.com>

>>>>

RL informed by natural language is a relatively new field, where research before 2018 have been limited to relatively small corpora or synthetic language \cite[1]{survey}. With the introduction of Large Language Models, many new possibilities have opened up, and in recent years there have been many successful integrations of these models into traditional RL \cite{omni} \cite{ellm} \cite{idm}.
